A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-19 sections/algorithm.tex
some non-overlapping text

>>>>

\subsection{Non-overlapping and Deterministic Reduction}
An interesting and important aspect of our algorithmic rules is that
they are directly implementable.
Although written in the form of reduction rules, they do not overlap with each other.
\jimmy{TODO: subtyping: $\forall$L with $\forall$R}
Rule 18 is the most general case for checking,
where its corresponding rule in DK's algorithm overlaps with all other checking rules.
We prevent the non-determinism by restricting the condition of Rule 18,
namely $e\neq\lam e'$ and $B\neq\all B'$.
In other words, Rules 19, 20 and 21 have higher priority to Rule 18 when implemented.
Thus our algorithm runs in polymorphic time, which is suitable for practical scenarios.

\jimmy{Describe how to achieve the non-overlapping: a proof of declarative system,
and then link to the metatheory for more details.}
